APBS \cite{Baker_2001} performs solvation free energy calculations using the Poisson-Boltzmann implicit solvent method.

Gromacs \cite{Pronk_2013} is a complete and well-established package for molecular dynamics simulations that provides high performance on both CPUs and GPUs.  It can be used for free energy and QM/MM calculations.

LAMMPS  (Large-scale Atomic/Molecular Massively Parallel Simulator) \cite{Plimpton_1995} is a highly modular classical molecular dynamics simulator that includes a diverse array of energy potentials and integrators.

lsfitpar \cite{Vanommeslaeghe_2015} derives bonded parameters for Class I force fields by performing a robust fit to potential energy scans provided by the user.

MDynaMix \cite{Lyubartsev_2000} is a basic general purpose molecular dynamics package.

MEPSA (Minimum Energy Pathway Analysis) \cite{Marcos_Alcalde_2015} provides tools for analyzing energy landscapes and pathways.

OpenMM  \cite{Eastman_2013} is a substantial toolkit for high performance molecular dynamics simulations that includes support for GPU acceleration.

PDB2PQR \cite{Dolinsky_2007} prepares structures for electrostatics calculations by adding hydrogens, calculating sidechain pKa, adding missing heavy atoms, and assigning force field-dependent parameters; users can specify an ambient pH.

PLUMED \cite{Tribello_2014} interfaces with an assortment of molecular dynamics software packages to provide a unified interface for performing free energy calculations using methods such as metadynamics, umbrella sampling and steered MD (Jarzynski).

PyRED \cite{Dupradeau_2010} generates RESP and ESP charges for the AMBER, CHARMM, OPLS, and Glycam and force fields.

yank is built off of OpenMM and provides Python interface for performing alchemical free energy calculations.