\paragraph{2D Desktop Applications (Table~\ref{2ddesktopviz})}

BKChem is a 2D molecular editor written in python that uses the Tk GUI toolkit.

chemfig is a tool for embedding chemical drawings in \LaTeX documents.

Chemtool is a 2D molecular editor for Linux systems that uses the GTK toolkit.

LeView \cite{Caboche_2013} generated 2D representations of ligand-protein interactions.

mol2chemfig \cite{Brefo_Mensah_2012} converts SMILES files into \LaTeX source code.

Molsketch is a 2D molecular editor written in C++ with the Qt toolkit that includes support for the Windows and Android operating systems.

SketchEl is a Java-based 2D molecular editor that includes support for a datasheet view for handling multi-molecule files.

QuteMol \cite{Tarini_2006} provides high-quality, visually engaging renderings of 3D molecular data.


\paragraph{3D Desktop Applications (Table~\ref{3ddesktopviz})}

Avogadro \cite{Hanwell_2012} is a 3D molecular viewer and editor with a modular plugin architecture with both Python and C++ bindings that includes interactive structure optimization for real-time editing. 

BALLView \cite{Moll_2005} provides interactive 3D visualizations as part of the BALL \cite{Hildebrandt_2010} cheminformatics toolkit.

Jamberoo provides a basic Java-based 3D molecular viewer and editor.

Luscus \cite{Kova_evi__2015} is a 3D viewer and editor that is designed with a focus on quantum chemical information.

OpenStructure \cite{Biasini_2013} is a computational structural biology framework that provides 3D viewer for manipulating structural information that includes an interactive Python shell.

PLIP (Protein-Ligand Interaction Profiler) \cite{Salentin_2015} runs as a web application and analyzes and visualizes protein-ligand interactions in 3D.

PyMOL is substantial 3D molecular viewer that includes a full Python interface to support scripting and plugin development.

RasTop and OpenRasMol are based off the venerable RasMol software and provide basic 3D visualization. 

\paragraph{Web-Based Visualization}

3Dmol.js \cite{Rego_2014} is a JavaScript library that provides WebGL-accelerated interactive 3D visualizations of molecular structures and surfaces.

CH5M3D \cite{Earley_2013} uses JavaScript and HTML5 to provide visualization and editing of 3D structures of small molecules.




