\section*{What is Open Source?}

Free and open-source software (FOSS) is software that is both considered ``free software,'' as defined by the Free Software Foundation (\url{http://fsf.org}) and ``open-source,'' as defined by the Open Source Initiative (\url{http://opensource.org}).  The distinctions between free and open-source software are largely philosophical  - the free software movement is primary motivated by user freedoms while the open source movement is more concerned with promoting an open development model to enhance software quality.  However, as a practical matter, especially with regards to scientific software, such distinctions remain philosophical rather than practical as the most popular software licenses are both free and open source.  

The unifying theme of open source software licenses is that they allow users to use, modify, and distribute software without significant restrictions.  This is achieved by making the full source code of the software available to users.  Broadly speaking, open source licenses fall into two categories: permissive and copyleft. Permissive licenses, such as the Apache, BSD, MIT, and Python licenses, place minimal restrictions on how modified code may be distributed, such as requiring attribution and limiting liability.  They specifically do not require that redistributions of modified source code be licensed under the same license as the original source code.  This enables source code licensed under a permissive license to be incorporated into commercial, proprietary programs that are not open source.  In contrast, copyleft licenses, such as the different versions of the GNU Public License (GPL), require that public redistributions of licensed software remain licensed under a GPL license.  That is, the source code must remain publicly and freely available. Although the GPL does not prohibit selling software, since the full source code must be freely available, in practice vendors of copylefted software must commercialize the support of the product, rather than the product itself.


\section*{Advantages and Disadvantages of Open Source}


Reference recent commentary \cite{Karthikeyan_2014}\cite{Gezelter_2015}\cite{Krylov_2015}
Advantages 
Free
Not a black box 
Can improve, extend, and incorporate
Reproducibility (reference royal society report)
Easy distribution (sourceforge, github)
Did we mention free?

Disadvantages
Difficult to commercialize (not a disadvantage from scientific standpoint, but has implications for users)
Support is often limited or nonexistent 
Development depends on active communities of user-developers 
Many packages are primarily developed/supported by a single person (concern about sustainability)
Modeling is a niche area not highly populated by programmers

Methodology for identifying software: click2drug.org, sourceforge, ??

Shoudl also investigate http://cheminformatics.org/
Evaluation criteria: license, development activity rating, usage, number of developers (active)

Categories:
 cheminformatics (putting toolkits in here), QSAR, visualization, docking, protein structure, protein dynamics, virtual screening, ??/
 
 
 How much evaluation are we going to do?  First look for existing articles.
 
 conformer generation - http://pubs.acs.org/doi/abs/10.1021/ci2004658 - but should update with enhancements to rdkit
 pharmacophore search - http://pubs.acs.org/doi/abs/10.1021/ci2005274
 docking - vina compared itself to autodock..
  
  
  \cite{Koes_2011}
  